### 2013-10-24 paper/main.tex
start draft of paper

```{r, echo=FALSE}
#Note, this needs the ashr library installed.
#To build the library run the following (from the Rcode subdirectory):
#require(devtools)
#install("../package/ashr")
#Then RESTART R before knitting the following code
```

### Project Goals

@@

### Methods Outline

@@

### The False Sign Rate

@@

As pointed out by Gelman et al, there are settings where
$\beta_j=0$ is implausible, in which case the lfdr is not
a useful concept: if every $\beta_j$ is non-zero then there
is no such thing as a false discovery and the lfdr will be 0. Gelman et al suggest that in such settings we
might replace the concept of a false discovery with the
concept of an "error in sign". The idea is that, in settings where $\beta_j=0$ is implausible, the most fundamental
inference objective is to ask which $\beta_j$ are positive and which are negative. Indeed, even in settings where some
$\beta_j$ are exactly zero, it could be argued that identifying which are positive and which negative is
fundamentally more interesting and useful than identifying which are non-zero. However, in such settings this usually comes down to something similar in practice: the observations that one can tell are non-zero are also the ones whose
sign can be reliably inferred. In this sense the
local false sign rate is a natural generalization of
the local false discovery rate.

Following these ideas of Gelman et al, we define the local False Sign Rate (lfsr) as 
$$\text{lfsr}_j = \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\beta, s) ].$$
To give the intuition behind this, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then, if we were to declare that $\beta_j$ is negative, the probability that we have
made an error in sign would be 0.05.

@@

### Computation Outline

@@

### Example 1: A simple simulated example to get started

Load in some functions.
```{r}
#setwd("~/Documents/git/ash/Rcode/")
set.seed(32327)

## load ashr library 
require("ashr")
require("qvalue")
```

```{r}
#simulate n beta-hat values, nnull under the null
#with altmean and altsd being the mean and sd of beta under the alternative
simdata=function(n, nnull, altmean, altsd, betasd){
  null = c(rep(1,nnull),rep(0,n-nnull))
  beta = c(rep(0,nnull),rnorm(n-nnull,altmean,altsd))
  betahat = rnorm(n,beta,betasd)
  return(list(null=null,beta=beta,betahat=betahat,betasd=betasd))
}
```

Simulate 10000 $\beta_j$ values, 8000 from a mixture of a point mass at 0 and
2000 from $\beta \sim N(0,sd=2)$.

```{r}
ss = simdata(10000,8000,0,2,1)

beta.ash=ash(ss$betahat,ss$betasd)
xmin = min(ss$beta)
xmax = max(ss$beta)
x=seq(xmin,xmax,length=1000)
plot(sort(ss$beta),(1:length(ss$beta))/length(ss$beta),main="cdf of ss$beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)

```

Compare with mixfdr. Note that I tried to do smaller than 1000, but mixfdr returned
errors. (Maybe this example is not so useful for comparing fdrs (as opposed to shrinkage), since the methods tend to agree where the fdr is small, which is what matters?)
```{r}
ss = simdata(1000,500,0,2,1)

beta.ash=ash(ss$betahat,ss$betasd)
beta.ash.u = ash(ss$betahat,ss$betasd, mixcompdist="uniform")
beta.ash.hu = ash(ss$betahat,ss$betasd, mixcompdist="halfuniform")

require(mixfdr)
beta.mfdr.J3 = mixFdr(ss$betahat,J=3,noiseSD=1,theonull=TRUE)
beta.mfdr.J5 = mixFdr(ss$betahat,J=5,noiseSD=1,theonull=TRUE)
beta.mfdr.J7 = mixFdr(ss$betahat,J=7,noiseSD=1,theonull=TRUE)
beta.mfdr.J9 = mixFdr(ss$betahat,J=9,noiseSD=1,theonull=TRUE)
beta.mfdr.J15 = mixFdr(ss$betahat,J=15,noiseSD=1,theonull=TRUE)
mean((beta.mfdr.J3$effectSize-ss$beta)^2)
mean((beta.mfdr.J5$effectSize-ss$beta)^2)
mean((beta.mfdr.J7$effectSize-ss$beta)^2)
mean((beta.mfdr.J9$effectSize-ss$beta)^2)
mean((beta.mfdr.J15$effectSize-ss$beta)^2)

mean((beta.ash$PosteriorMean-ss$beta)^2)
mean((beta.ash.u$PosteriorMean-ss$beta)^2)
mean((beta.ash.hu$PosteriorMean-ss$beta)^2)

#This code mostly borrowed from the examples in mixFdr in R help
m=beta.mfdr.J15
mTrue = list(pi=c(0.8,0.2),mu=c(0,0),sig=c(1,2))
par(mfcol=c(1,1))
s = seq(-5,5,by=0.01)
trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.002) # this tells it which indices to consider null
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))
 lines(s, fdrCurve, col = 2)
points(ss$betahat,beta.ash$localfdr,col=3)
points(ss$betahat,beta.ash.u$localfdr,col=4)
points(ss$betahat,beta.ash.hu$localfdr,col=5)

```

Of course, if we do something where alternatives are not centered on 0 then
ash does worse!
```{r}
#This is the example from the mixfdr help example
z = c(rnorm(1000), rnorm(100,3,1))
 m = mixFdr(z, J = 3, noiseSD = 1)
 s = seq(-5,5,by=0.01)
 effCurve = effectSize(s,m)[,1]
 fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.2) # this tells it which indices to consider null

# compare to the Bayes estimator for this problem
 mTrue = list(pi = c(10,1)/11, mu = c(0,3), sig = c(1,1))
# note that the model parameters are in terms of the MARGINAL not of the prior
 trueEff = effectSize(s,mTrue)[,1]
 trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
 par(mfrow = c(2,1))
 plot(s, trueEff, t = 'l', main = "Effect Size - Black is true", xlab = "z", ylab = "E(delta|z)", ylim = c(-3,3))
 lines(s, effCurve, col = 2)
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))

z.ash = ash(z,1,mixcompdist="halfuniform")
points(z,z.ash$localfdr,col=3)
```

Checking coverage
```{r}

```

@@

## The number of components is not critical

OR - this section could be more generally about selecting between
models (normal, uniforms etc) using log-likelihood.

@@

The following example illustrates this.
We take 100 observations from 0.5N(-1,1)+0.5N(1,1)
and add N(0,1) noise.
```{r}
set.seed(200)
sampsize=50
beta = c(rnorm(sampsize,-1,1),rnorm(sampsize,1,1))
betahat = beta+rnorm(2*sampsize)

beta.ash.default = ash(betahat,1) #run with default parameters for comparison
beta.ash.vb.default = ash(betahat,1,VB=TRUE) #run with default parameters for comparison

beta.ash.100 = ash(betahat,1,mixsd = seq(0.1,5,length=100))
beta.ash.100u = ash(betahat,1,mixcompdist="uniform",mixsd = seq(0.1,5,length=100))
beta.ash.100hu = ash(betahat,1,mixcompdist="halfuniform",mixsd = seq(0.1,5,length=100))

beta.ash.vb.100 = ash(betahat,1,mixsd = seq(0.1,5,length=100),VB=TRUE)
beta.ash.vb.100u = ash(betahat,1,mixcompdist="uniform",mixsd = seq(0.1,5,length=100),VB=TRUE)
beta.ash.vb.100hu = ash(betahat,1,mixcompdist="halfuniform",mixsd = seq(0.1,5,length=100),VB=TRUE)

x=seq(-4,4,length=1000)
plot(x,0.5*dnorm(x,-1,1)+0.5*dnorm(x,1,1),col=1,ylim=c(0,0.45),main="Fitted densities vs truth",type="l",ylab="density")
lines(x,density(beta.ash.default,x),col=2)
lines(x,density(beta.ash.100,x),col=2)
lines(x,density(beta.ash.100u,x),col=3)
lines(x,density(beta.ash.100hu,x),col=4)

plot(x,0.5*dnorm(x,-1,1)+0.5*dnorm(x,1,1),col=1,ylim=c(0,0.45),main="Fitted densities (VB) vs truth",type="l",ylab="density")
lines(x,density(beta.ash.vb.default,x),col=2)
lines(x,density(beta.ash.vb.100,x),col=2,lty=2)
lines(x,density(beta.ash.vb.100u,x),col=3,lty=2)
lines(x,density(beta.ash.vb.100hu,x),col=4,lty=2)

plot(x,0.5*pnorm(x,-1,1)+0.5*pnorm(x,1,1),col=1,main="Fitted cdfs vs truth",type="l",ylab="density")
lines(x,cdf.ash(beta.ash.100,x),col=2,lty=2)
lines(x,cdf.ash(beta.ash.100u,x),col=3,lty=2)
lines(x,cdf.ash(beta.ash.100hu,x),col=4,lty=2)

plot(x,0.5*pnorm(x,-1,1)+0.5*pnorm(x,1,1),col=1,main="Fitted cdfs (VB) vs truth",type="l",ylab="density")
lines(x,cdf.ash(beta.ash.vb.default,x),col=2,lty=2)
lines(x,cdf.ash(beta.ash.vb.100,x),col=2,lty=2)
lines(x,cdf.ash(beta.ash.vb.100u,x),col=3,lty=2)
lines(x,cdf.ash(beta.ash.vb.100hu,x),col=4,lty=2)

c(loglik.ash(beta.ash.100,betahat,1),get_loglik(beta.ash.100u),get_loglik(beta.ash.100hu))
c(loglik.ash(beta.ash.vb.100,betahat,1),loglik.ash(beta.ash.vb.100u,betahat,1),loglik.ash(beta.ash.vb.100hu,betahat,1))

rmse=function(a,b){sqrt(mean((a$PosteriorMean-b)^2))}
c(rmse(beta.ash.default,beta),rmse(beta.ash.100,beta),rmse(beta.ash.100u,beta),rmse(beta.ash.100hu,beta),rmse(beta.ash.vb.default,beta),rmse(beta.ash.vb.100,beta),rmse(beta.ash.vb.100u,beta),rmse(beta.ash.vb.100hu,beta))

plot(beta.ash.default$PosteriorMean,beta.ash.100u$PosteriorMean,col=3,cex=0.4,xlim=c(-4,4),ylim=c(-4,4))
points(beta.ash.default$PosteriorMean,beta.ash.100hu$PosteriorMean,col=4,cex=0.4)
abline(a=0,b=1)

plot(betahat,ifelse(pnorm(betahat)<0.5,pnorm(betahat),1-pnorm(betahat)))
points(betahat,beta.ash.default$localfsr,col=2)
points(betahat,beta.ash.100u$localfsr,col=3)
points(betahat,beta.ash.100hu$localfsr,col=4)

```

so it seems that the localfsr is almost the same as for a "flat" prior $g$.
That is, in this case, the underlying distribution is flat relative to the
error terms, and so there is little shrinkage effect except at the tails
(where the fsr is basically 0 anyway).

```{r}
sampsize=5000
beta = c(rnorm(sampsize,-1,1),rnorm(sampsize,1,1))
betahat = beta+rnorm(2*sampsize)

beta.ash = ash(betahat,1)
beta.ash.u=list()
for(i in 1:10){
  beta.ash.u[[i]] = ash(betahat,1,mixcompdist="uniform",mixsd = seq(0.1,5,length=10*i))
}

plot(beta.ash,-4,4,col=2)
x=seq(-4,4,length=1000)
lines(x,0.5*dnorm(x,-1,1)+0.5*dnorm(x,1,1),col=1)
for(i in 1:4){
lines(x,density(beta.ash.u[[i]],x),col=2+i)
}

plot(unlist(lapply(beta.ash.u,ashr:::get_loglik)))

```

```{r}
ss = simdata(10000,8000,0,2,1)

beta.ash=ash(ss$betahat,ss$betasd,auto=FALSE)
beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)
#these to test the VB version 
beta.ash.vb.uniform = ash(ss$betahat, ss$betasd,VB=TRUE, prior="uniform")
beta.ash.vb.nullbiased = ash(ss$betahat, ss$betasd,VB=TRUE, prior="nullbiased")

beta.ash.pm = ash(ss$betahat,ss$betasd,usePointMass=TRUE)

#compute the usual zscore and corresponding p value
zscore = ss$betahat/ss$betasd

pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
hist(zscore)
```

Plot the fitted underlying distribution on top of true values for beta
```{r}
hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-7,7,length=1000)
lines(x,density(beta.ash,x),col=2)

plot(sort(ss$beta),(1:length(ss$beta))/length(ss$beta),main="cdf of ss$beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)
lines(x,cdf.ash(beta.ash.auto,x),col=3,lwd=2)
lines(x,cdf.ash(beta.ash.vb.uniform,x),col=4,lwd=2)
lines(x,cdf.ash(beta.ash.vb.null,x),col=5,lwd=2)
lines(x,cdf.ash(beta.ash.pm,x),col=6,lwd=2)
```

[for testing: compare results with point mass and without]
```{r}
  plot(beta.ash$PositiveProb)
  points(beta.ash.pm$PositiveProb,col=2)
```

```{r}
  plot(beta.ash$ZeroProb)
  points(beta.ash.pm$ZeroProb,col=2)
```

[for testing: compare with the results from the automatic way for selecting sigma]
```{r}
hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-4,4,length=1000)
lines(x,density(beta.ash.auto,x),col=2)
```

[for testing: note that the PosteriorMean and PositiveProb don't depend much on sigmaa vec used ]

```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from fixed method")
abline(a=0,b=1)
plot(beta.ash.auto$localfdr, beta.ash$localfdr, xlab="lfdr from auto method", ylab="ldfr from fixed method")
abline(a=0,b=1)

```

[And VB method produces similar results to EM method]
```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash.vb.uniform$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from vb method")
points(beta.ash.auto$PosteriorMean, beta.ash.vb.null$PosteriorMean, col=2)
abline(a=0,b=1)
plot(beta.ash.auto$localfdr, beta.ash.vb.uniform$localfdr, xlab="lfdr from auto method", ylab="ldfr from vb method")
points(beta.ash.auto$localfdr, beta.ash.vb.null$localfdr, col=2)
abline(a=0,b=1)

```

Also, we can see the effects of shrinkage: small estimates of $\hat\beta$ are
shrunk to close to 0. Large estimates of $\hat\beta$ are shrunk less strongly because ash recognizes that these larger $\hat\beta$ are likely
from the alternative, rather than the null.
```{r}
plot(ss$betahat,beta.ash$PosteriorMean,xlab="Observed betahat", ylab="Estimated beta (posterior mean)",ylim=c(-7,7),xlim=c(-7,7))
abline(h=0)
abline(a=0,b=1,col=2)
```

### Some additional notes

#### Do we need a point mass at zero?

@@

#### Comparison with qvalue

Here we compare ash $q$ values with those from the qvalue package. 
```{r}
plot(qval$q,beta.ash$qval,main="comparison of ash and q value qvalues",xlab="qvalue", ylab="ash q values")
abline(a=0,b=1)
```

In this example we see that qval overestimates the actual FDR. (This
is because it assumes all the $p$ values near 1 are null, when they are not.)
```{r}
o = order(beta.ash$qval)
plot(cumsum(ss$null[o])/(1:10000),qval$qval[o],col=2,type="l", xlab="actual FDR", ylab="q value", main="Comparison of actual FDR with q value")
lines(cumsum(ss$null[o])/(1:10000),beta.ash$qval[o])
abline(a=0,b=1)
```

### Miscellaneous

code and text below here is work in progress and untidied.

Here we simulate data, effectively as in Efron, 2008, Section 7.
```{r}
truenull = c(rep(0,1000),rep(1,9000))
beta = c(rnorm(1000,-3,1),rep(0,9000))
s= rep(1,10000)
betahat = rnorm(10000,beta,s)

beta.ash=ash(betahat,s)
#compute the usual zscore and corresponding p value
zscore = betahat/s
pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)

plot(betahat,beta.ash$PosteriorMean,xlab="Observed betahat", ylab="Estimated beta (posterior mean)",ylim=c(-7,7),xlim=c(-7,7))
abline(h=0)
abline(a=0,b=1,col=2)

plot(qval$q,beta.ash$qval,main="comparison of ash and q value qvalues")
abline(a=0,b=1)

o = order(beta.ash$qval)

plot(cumsum(truenull[o])/(1:10000),qval$qval[o],col=2,type="l")
lines(cumsum(truenull[o])/(1:10000),beta.ash$qval[o])
abline(a=0,b=1)
```

It seems that in this case the ash q values underestimate the
FDR slightly. Possibly this is the assymetry.
Try shrinking positive and negatives separately:
```{r}
pos= betahat>0
betapos.ash=ash(betahat[pos],s[pos])
betaneg.ash = ash(betahat[!pos],s[!pos])
lfdr = rep(0,length(betahat))
lfdr[pos] = betapos.ash$localfdr
lfdr[!pos] = betaneg.ash$localfdr
qv = qval.from.localfdr(lfdr)
o = order(qv)
plot(cumsum(truenull[o])/(1:10000),qv[o],type="l")
abline(a=0,b=1)
```
No, that's not it.

So maybe it is the non-monotonic behaviour of the true beta values in this case.
Let's try putting in a component at -1.5 to make the data fit this assumption better.

### Illustration of halfuniform method

I will also use this to illustrate the halfuniform method, which
allows for asymmetry.

```{r}
truenull = c(rep(0,2000),rep(1,8000))
beta = c(rnorm(1000,-3,1),rnorm(1000,-1.5,1),rep(0,8000))
s= rep(1,10000)
betahat = rnorm(10000,beta,s)

beta.ash=ash(betahat,s)
beta.ash.halfu = ash(betahat,s,"halfuniform")

hist(beta,prob=TRUE)
x = seq(-8,4,length=1000)
lines(x,density(beta.ash,x),col=2)
lines(x,density(beta.ash.halfu,x),col=3)

```

See how the use of the asymmtric uniform component does a better job capturing
the underlying density. Probably clearer in the cdf plot:
```{r}
plot(sort(beta),(1:length(beta))/length(beta),main="cdf of beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)
lines(x,cdf.ash(beta.ash.halfu,x),col=3,lwd=2)

#compute the usual zscore and corresponding p value
zscore = betahat/s
pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
plot(qval$q,beta.ash$qval,main="comparison of ash and q value qvalues")
abline(a=0,b=1)

o = order(qval$qval)
plot(cumsum(truenull[o])/(1:10000),qval$qval[o],col=1,type="l")
o = order(beta.ash$qval)
lines(cumsum(truenull[o])/(1:10000),beta.ash$qval[o],col=2)
o2 = order(beta.ash.halfu$qval)
lines(cumsum(truenull[o2])/(1:10000),beta.ash.halfu$qval[o2],col=3)

abline(a=0,b=1)

```

### Motivation

@@

>>>>

% Template for PLoS
% Version 1.0 January 2009
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template

\documentclass[10pt]{article}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

% Use the PLoS provided bibtex style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

\pagestyle{myheadings}
%% ** EDIT HERE **
\usepackage{enumerate}
\usepackage{multirow} 
\usepackage{url}
\usepackage{xr} %for cross-referencing
%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\newtheorem{algorithm}{Algorithm}
\newtheorem{proposition}{Proposition}
\newtheorem{restateproposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{result}{Result}
\newtheorem{note}{Note}
\newtheorem{definition}{Definition}

\def\x{\mbf{x}}
\def\y{\mbf{y}}
\def\e{\mbf{e}}
\def\g{\mbf{g}}
\def\p{p}
\def\Yb{\hat{Y}_1^{\text{BAYES}}}
\def\Xperp{X_{1 \perp 0}}
\def\Pperp{P_{1 \perp 0}}
\def\Pperpb{\Pperp^{\text{B}}}
\def \hatd { \widehat{ d } }
\def \dhatin {\hatd^{\mbox{\tiny IN}}}
\def \dhatsw {\hatd^{\mbox{\tiny SW}}}
\def \mvn{\text{MVN}}
\def\mn{\text{MN}}
\def \iw{\text{W}^{-1}}
\def \fp {fastPHASE\ }
\def\var{\rm Var}
\def\mvr{\text{BMVR}}
\def\bfuni{\text{BF}_\text{uni}}
\def\one{\mbf{1}}
\def\zero{\mbf{0}}
\def\hall{H_{\text{all}}}
\def\pall{\p_{\text{all}}}
\def\bfall{\text{BF}_\text{all}}
\def\bfav{\text{BF}_\text{av}}
\def\gall{\gamma_\text{all}}
\def\limbfall{\bfall^\rightarrow}
\def\limbfav{\bfav^\rightarrow}
\def\limbfgamma{\BF_\gamma^\rightarrow}
\def\sxx{S_{xx}}
\def\syy{S_{yy}}
\def\vyy{V_{yy}}
\def\vyx{V_{yx}}
\def\vxx{{V_{xx}}}
\def\rss{\text{\rm RSS}}
\def\dss{\text{\rm $\Delta$SS}}
\def\U{U}
\def\D{D}
\def\I{I}
\def\luu{L_{UU}}
\def\indep{\perp}
\newcommand{\mbf}[1]{\mbox{\boldmath$#1$}} % true mathbf works in math
                                % mode too
\newcommand\height{{\it height}}
\newcommand\weight{{\it weight}}
\def\BF{\text{BF}}

%% END MACROS SECTION
\externaldocument{plos_one_rev1_suppinfo}

\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Shrinkage, False Discovery Rate Estimation, and an alternative to the ``Zero assumption" when precision varies across units}
}
% Insert Author names, affiliations and corresponding author email.
\\
Matthew Stephens$^{1*}$, 
\\
\bf{1} Department of Statistics and Department of Human Genetics, University of Chicago, Chicago, IL, USA
\\
$\ast$ E-mail: Corresponding mstephens@uchicago.edu
\end{flushleft}

% Please keep the abstract between 250 and 300 words
\section*{Abstract}

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
%\section*{Author Summary}

\section*{Introduction}

Suppose that we measure, with error, a series of ``effects", $\beta_1,\dots,\beta_J$. To take just one concrete 
example, $\beta_j$ could be 
the difference in the mean (log) expression levels of gene $j$ ($j=1,\dots,J$) between 2 conditions. In this case, a measurement of
the effect might be the difference in sample means obtained in the two conditions. We will let $\hat\beta_j$ denote the measured value of $\beta_j$, and assume that
each measurement comes with an associated standard error, 
$s_j$. A key aim here will be to take proper account of the fact that some measurements may be more precise than others: that is, to take proper account of variation in $s_j$ across $j$.

A common goal, particularly in genomic studies, is to identify which $\beta_j$ differ from zero. This is commonly tackled
by first computing a $p$ value for each $j$, testing $H_j:\beta_j=0$, and then applying methods based on False Discovery Rates, such as the qvalue package. For example, we could compute $Z$ scores $Z_j = \beta_j/s_j$, and translate $Z_j$ to a $p$ value, 
$p_j$, and then use now-standard methods to select a $p$ value threshold to control the FDR.

There are two issues with this approach that I would like to address here. The first is that it really does not take proper account of the measurement errors. To see this, consider an example where half the measurements are quite precise, and the other half are really, really, poor. Intuitively, the poor measurements tell us nothing, and any sane analysis should effectively ignore them. However, in a standard FDR-type analysis, these poor measurements add ``noise" and affect estimated FDRs. This is because the $p$ values from the poor measurements will be effectively uniformly distributed, and some will be significant at any given threshold.

@@

 \section*{Methods}

 The two main assumptions we will make here are that 
* these effects are exchangeable: that is (by de Finetti's theorem) they can be
thought of as being independent and identically distributed from some unknown distribution $g(\beta)$. 
* these effects are symmetrically distributed about 0, with density monotonically decaying as we move away from 0.

Specifically we will assume a parameteric form for $g$
as a mixture of 0-centered normal distributions

A key issue I want to address here is that if these measurements are made with different precisions, then we want to
take this into account in our analysis.
We can do this by assuming that the likelihood for $\beta$ is a normal, with mean $\hat\beta_p$ and standard deviation $s_p$. (Note that this is equivalent to the likelihood we would get
if we ``observed" data $\hat\beta_p \sim N(\beta_p, s_p)$.)

@@

\subsection{The False Sign Rate}

@@

As pointed out by \cite{gelman.etal}, there are settings where
$\beta_j=0$ is implausible, in which case the lfdr is not
a useful concept: if every $\beta_j$ is non-zero then there
is no such thing as a false discovery and the lfdr will be 0. Gelman et al suggest that in such settings we
might replace the concept of a false discovery with the
concept of an "error in sign". The idea is that, in settings where $\beta_j=0$ is implausible, the most fundamental
inference objective is to ask which $\beta_j$ are positive and which are negative. Indeed, even in settings where some
$\beta_j$ are exactly zero, it could be argued that identifying which are positive and which negative is
fundamentally more interesting and useful than identifying which are non-zero. However, in such settings this usually comes down to something similar in practice: the observations that one can tell are non-zero are also the ones whose
sign can be reliably inferred. In this sense the
local false sign rate is a natural generalization of
the local false discovery rate.

Following these ideas of \cite{gelman.etal}, we define the local False Sign Rate (lfsr) as 
$$\text{lfsr}_j = \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\beta, s) ].$$
To give the intuition behind this, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then, if we were to declare that $\beta_j$ is negative, the probability that we have
made an error in sign would be 0.05.

@@

\subsection{Computation Outline}

@@

\section*{Results}

- Illustration that 2 local false sign rate is approximately local fdr.

- Illustration of effects of contamination on FDR by low-quality data
comparison with ash.

- Illustration of the difference between the zero assumption and no zero assumption on FDR
in case z is N(0,2) vs N(0,1). [no difference in precision]

- Comparison between exchangeable effects vs Exchangeable standardized effects; Hedenberg data.

- Possibly difference between CIs obtained by ash and usual CIs (e.g. ``of intervals where local fsr is <0.05, what proportion are the sign correct"?).

- Asymmetric case (Half uniforms)

@@

\subsection{The number of components is not critical}
OR - this section could be more generally about selecting between
models (normal, uniforms etc) using log-likelihood.

@@

\subsection{Do we need a point mass at zero?}

@@

\subsection{Side notes on Multiple comparisons}

@@

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}

Statistical analyses were conducted in the {\sf R} programming language \cite{Rcore:2012}, Figures produced using the ggplot2 package \cite{ggplot2}, and text
prepared using \LaTeX.

%\section*{References}
% The bibtex filename
\bibliography{/Users/stephens/Documents/mainbib}

\section*{Figure Legends}

\clearpage

\section*{Tables}

\section*{Supporting Information Legends}

Supplementary material can be found in {\bf Supplementary Information S1.}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

\end{document}
